---
title: "Mediation Analysis"
author: ""
date: '24 10 2022'
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Libraries


```{r library, include=FALSE}
library(tidyverse)
library(lme4)
library(rcompanion)
library(car)
library(texreg)
library(ggeffects)
library(xtable)
library(scales)
library(MASS)
library(glmmTMB)
library(brglm2)
library(reshape2)
library(mediation)
#library(broom.mixed)
library(performance)
source("utils.R")

```


# Import Data


```{r data, include=FALSE}
df <- read_csv("data/df_cascades_preprocessed.csv")
```


## Filter out potential NAs

```{r message=F, warning=F}

df_filtered <- df %>%
  drop_na(root_account_age)

sum(is.na(df_filtered$root_account_age))
sum(is.na(df_filtered$tweet_count_byage))
sum(is.na(df_filtered$listed_count_byage))

```


# Scaling

```{r message=F, warning=F}

vars_to_standardize <- c("cascade_size", "cascade_lifetime", "cascade_structural_virality", "sentiment", "followers_count", "following_count", "tweet_count", "root_account_age", "tweet_count_byage", "tweet_length", "tweet_uncleaned_length")

df_filtered_scaled <- df_filtered %>%
  mutate_at(vars(matches(paste0(vars_to_standardize, collapse = "|"))),
            funs(log = log(1 + .))) %>%
  mutate_at(vars(matches(paste0(vars_to_standardize, collapse = "|"))),
            .funs = funs(scaled = scale(.) %>% as.vector))

```

# Variable definitions

```{r, echo=F}
variable_definitions <- tribble(
  ~ModelVariable, ~DisplayVariable,  ~Description,
  "maj_label", "Majority label", "The label given to the specific tweet (hate or normal)",
  "hate_dummy", "Hateful", "If tweet is hateful (1 if true, otherwise 0)",
  "cascade_size", "Cascade size", "Number of unique users involved in a cascade",
  "cascade_lifetime", "Cascade lifetime", "Time difference between the last retweet and the cascade's original tweet (in hours)",
  "cascade_structural_virality", "Structural virality", "The average distance between all pairs of nodes in a cascade",
  "media_dummy", "Media item", "If tweet contains a URL-link and/or an attachment (1 if true, otherwise 0)",
  "mention_dummy", "Mention", "If tweet mentions another user (1 if true, otherwise 0)",
  "directed_dummy", "Directed", "If tweet mentions another user and contains 2nd pronouns (1 if true, otherwise 0)",
  "hashtag_dummy", "Hashtag", "If tweet contains a hashtag (1 if true, otherwise 0)",
  "tweet_length", "Tweet length", "The number of characters in the tweet",
  "verified_dummy", "Verified", "If tweet-author is verified by twitter (1 if true, otherwise 0)",
  "root_account_age", "Account age", "The age of the root-author’s account (in days)",
  "root_account_age_in_1000", "Account age (in 1000s)", "The age of the root-author’s account (in 1000 days)",
  "tweet_count_byage", "Tweet volume", "The number of tweets the root-author has made devided by the Account Age (in days)",
  "followers_count", "Followers", "Number of people who follow the root-author on Twitter",
  "following_count", "Followees", "Number of people who the root-author follows on Twitter",
  "followers_count_in_1000", "Followers (in 1000s)", "Number of people who follow the root-author on Twitter (in 1000s)",
  "following_count_in_1000", "Followees (in 1000s)", "Number of people who the root-author follows on Twitter (in 1000s)",
)
```



# Mediation Analysis
## 1. Do the EVs significantly explain cascade lifetime and structural virality?
### Cascade lifetime


```{r}

control_vs_2d <- c("media_dummy", "verified_dummy", "followers_count_scaled", "following_count_scaled", "tweet_count_byage_scaled",  "root_account_age_scaled", "hashtag_dummy", "mention_dummy", "tweet_length_scaled")
interaction_vs_2d <- c()
exo_v_2d <- "hate_dummy"
dep_v_2d <- "cascade_lifetime_log"

model_2d <- lm(make_formula(dep_v_2d, c(control_vs_2d, exo_v_2d, interaction_vs_2d), c()), data = df_filtered_scaled)
```


```{r message=F, warning=F}

summary(model_2d)

```


### Cascade Structural Virality


```{r}

control_vs_3d <- c("media_dummy", "verified_dummy", "followers_count_scaled", "following_count_scaled", "tweet_count_byage_scaled",  "root_account_age_scaled", "hashtag_dummy", "mention_dummy", "tweet_length_scaled")
interaction_vs_3d <- c()
exo_v_3d <- "hate_dummy"
dep_v_3d <- "cascade_structural_virality_log"

model_3d <- lm(make_formula(dep_v_3d, c(control_vs_3d, exo_v_3d, interaction_vs_3d), c()), data = df_filtered_scaled)
```



```{r message=F, warning=F}

summary(model_3d)

```


## 2. Do the EVs significantly explain the mediator cascade size?


```{r}

control_vs_1d <- c("media_dummy", "verified_dummy", "followers_count_scaled", "following_count_scaled", "tweet_count_byage_scaled",  "root_account_age_scaled", "hashtag_dummy", "mention_dummy", "tweet_length_scaled")
interaction_vs_1d <- c()
exo_v_1d <- "hate_dummy"
dep_v_1d <- "cascade_size_log"

model_1d <- glm(make_formula(dep_v_1d, c(control_vs_1d, exo_v_1d, interaction_vs_1d), c()), data = df_filtered_scaled, family = Gamma(link = "log"))
```


```{r message=F, warning=F}

summary(model_1d)

```


## 3. How do the effects of EVs on cascade lifetime and structural virality change when controlling for mediator cascade size
### Cascade lifetime


```{r}

control_vs_2e <- c("media_dummy", "verified_dummy", "followers_count_scaled", "following_count_scaled", "tweet_count_byage_scaled",  "root_account_age_scaled", "hashtag_dummy", "mention_dummy", "tweet_length_scaled", "cascade_size_log")
interaction_vs_2e <- c()
exo_v_2e <- "hate_dummy"
dep_v_2e <- "cascade_lifetime_log"

model_2e <- lm(make_formula(dep_v_2e, c(control_vs_2e, exo_v_2e, interaction_vs_2e), c()), data = df_filtered_scaled)
```


```{r message=F, warning=F}

summary(model_2e)

```


### Cascade Structural Virality


```{r}

df_filtered_scaled <- df_filtered_scaled %>%
  mutate(
    cascade_structural_virality_log2 = log(1.1 + cascade_structural_virality),
    cascade_structural_virality_plus1 = 1 + cascade_structural_virality
  )

control_vs_3e <- c("media_dummy", "verified_dummy", "followers_count_scaled", "following_count_scaled", "tweet_count_byage_scaled",  "root_account_age_scaled", "hashtag_dummy", "mention_dummy", "tweet_length_scaled", "cascade_size_log")
interaction_vs_3e <- c()
exo_v_3e <- "hate_dummy"
dep_v_3e <- "cascade_structural_virality_log"

model_3e <- lm(make_formula(dep_v_3e, c(control_vs_3e, exo_v_3e, interaction_vs_3e), c()), data = df_filtered_scaled)
```



```{r message=F, warning=F}

summary(model_3e)

```


## 4. Statistically test mediation
### Cascade lifetime


```{r message=F, warning=F}

set.seed(1234)
results <- mediate(model_1d, model_2e, treat = "hate_dummy", mediator = "cascade_size_log", covariates = control_vs, boot = TRUE, sims = 500)
summary(results)

```

### Structural Virality


```{r message=F, warning=F}

set.seed(1234)
results <- mediate(model_1d, model_3e, treat = "hate_dummy", mediator = "cascade_size_log", covariates = control_vs, boot = TRUE, sims = 500)
summary(results)

```